ANOVA Comparison Simulations: Skewed, Poisson Data

### 2016-12-07 simulations/simulation_skewed.Rmd
Create 2 by 2 plot of power curves for different simulations

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      tidy = TRUE, tidy.opts = list(width.cutoff = 60),
                      cache = TRUE)
#devtools::install_github("statlab/permuter")
require(permuter)
require(dplyr)
require(reshape2)
require(ggplot2)
require(xtable)
options(xtable.comment = FALSE, xtable.include.rownames = FALSE, xtable.align = "p{3.5cm}")
require(grid)
require(gridExtra)
```

@@

```{r final_summary, fig.align = "center"}
grid.arrange(p1, p2, p4, p5)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      tidy = TRUE, tidy.opts = list(width.cutoff = 60),
                      cache = TRUE)
#devtools::install_github("statlab/permuter")
require(permuter)
require(dplyr)
require(reshape2)
require(ggplot2)
require(xtable)
options(xtable.comment = FALSE, xtable.include.rownames = FALSE, xtable.align = "p{3.5cm}")
require(grid)
require(gridExtra)
require(gtable)
```

@@

```{r final_summary, fig.align = "center"}
#plots4 <- lapply(list(p1, p2, p4, p5), function(pl) pl + theme(legend.position = "none") + ggtitle(""))
#do.call(grid.arrange, plots4)

powers <- list(design1_power %>% as.data.frame() %>% mutate("Treatment" = rep("Constant Additive Effect", nrow(design1_power)), "Design" = rep("Balanced", nrow(design1_power))), 
               design2_power %>% as.data.frame() %>% mutate("Treatment" = rep("Single Site Effect", nrow(design2_power)), "Design" = rep("Balanced", nrow(design2_power))), 
               design4_power %>% as.data.frame() %>% mutate("Treatment" = rep("Constant Additive Effect", nrow(design4_power)), "Design" = rep("Imbalanced", nrow(design4_power))), 
               design5_power %>% as.data.frame() %>% mutate("Treatment" = rep("Single Site Effect", nrow(design5_power)), "Design" = rep("Imbalanced", nrow(design5_power))))

all_power_curves <- do.call(rbind, powers)
twobytwo <- melt(all_power_curves, id.vars = c("Treatment", "Design")) %>% 
  mutate("pvalue" = rep((1: 100)/100, 5*4)) %>%
  mutate("Method" = variable) %>%
  ggplot(aes_string(x = "pvalue", y = "value", color = "Method")) +
  geom_line() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  xlab("P-value") +
  ylab("Power") +
  facet_wrap(Treatment~Design) +
  ggtitle("Discrete, Skewed Data")

twobytwo
```
